\clearpage
\centering
\vspace*{-\toptafiddle}

\textsc{Abstract of the Dissertation} \\~\\

\SingleSpacing{}

\thetitle{} \\~\\
by \\~\\
\theauthor{} \\~\\

\thedegree, Graduate Program in \thefield{} \\
\theuniversity{}, \thedate{} \\
\thechair{} \\~\\

\justify{}
\DoubleSpacing{}
Recent focus on two dimensional materials and spin-coupled phenomena
holds future potential for fast, efficient, flexible, and transparent devices.

The fundamental operation of a spintronic device
depends on the injection, transmission, and detection
of spins in a conducting channel.
Long spin lifetimes during transit are critical for realizing this technology.
An attractive platform for this purpose is graphene, which has high mobilities
and low spin-orbit coupling.
Unfortunately, measured spin lifetimes are orders of magnitude smaller
than theoretically expected.
A source of spin loss is the resistance mismatch between
the ferromagnetic electrodes and graphene.
While this has been studied numerically,
here we provide a closed form expression for Hanle spin precession
which is the standard method of measuring spin lifetimes.
This allows for a detailed characterization of the nonlocal spin valve device.

Strong spin orbit interaction has the potential
to engender unconventional superconducting states.
A cousin to graphene, two dimensional transition metal dichalcogenides
entwine interaction, spin-orbit coupling, and topology.
The noninteracting electronic states have
multiple valleys in the energy dispersion
and are topologically nontrivial.
We report on the possible superconducting states
of hole-doped systems, and analyze to what extent the correlated phase
inherits the topological aspects of the parent crystal.
We find that local attractive interactions or proximal coupling to
$s$-wave superconductors lead to a pairing
which is an equal mixture of a spin singlet and the $m = 0$ spin triplet.
Its topology allows quasiparticle excitations
of net nonzero Berry curvature via pair-breaking by circularly polarized light.
The valley contrasting optical response,
where oppositely circularly polarized light couples to different valleys,
is present even in the superconducting state, though with smaller magnitude.

\enlargethispage{\bottafiddle}
\clearpage
