\clearpage
\centering
\vspace*{-\toptafiddle}

\textsc{Acknowledgments}

\justify{}
\DoubleSpacing{}
I wish to express my immense gratitude to my adviser Dr.\ Vivek Aji,
who guided my work, but always left space to solve things my own way.
I am truly fortunate to have found a passionate and amiable adviser.
He always has an answer to my questions (with corresponding references),
and is quickly able to pick out the critical physics
needed to carry on whenever I get stuck.

Deep thanks to my committee members,
Dr.\ Nathaniel Gabor and Dr.\ Leonid Pryadko,
and my qualifying exam committee members,
Dr.\ Shan-Wen Tsai and Dr.\ Gregory Beran,
for supporting, questioning,
and helping me realize the wider impact of my work.
This work would not be possible without the strong collaboration
of our research group members, Dr.\ Huazhou Wei, Michael Phillips,
and Dr.\ Junhua Zhang.

Thanks to my undergraduate institution,
the College of Creative Studies at
the University of California, Santa Barbara,
for forging my beginnings as a physicist
and granting me the Regents Scholarship.
Thank you to the University of California, Riverside,
for supporting my work though the
Chancellor's Distinguished Fellowship Award,
Dr.\ Umar Mohideen, for heading and growing our physics department,
and Derek Beving, for navigating me though any administrative mazes.

The bulk of this work was originally published in
Physical Review Letters
\cite{%
  PhysRevB.89.245436,%
  1512.01261v2%
}.
The software developed
and used~\cite{Hunter:2007} for this work
and the included figures is available freely online.%
\footnote{%
  Related software and source code at \\
  \url{https://evansosenko.com/spin-lifetime}
  \\
  and \url{https://evansosenko.com/dichalcogenides}
}
We acknowledge useful discussions with
Adrian Swartz, Sung-Po Chao, and Roland Kawakami,
who made his research data available for general use.
We recognize the support of a UCR Senate Research Grant,
two GSA Conference Travel Grants,
and the Army Research Office through the grant
ARO W911NF1510079.

Finally, I would like to thank my fellow grads, friends, family, and parents
for their unwaivering and positive support of my intellectual pursuits.
\enlargethispage{\bottafiddle}
\clearpage
